### 2016-11-08 paper2.tex
Shuffled and resized figures

\begin{figure*}

    \includegraphics[width=\textwidth]{figures2/stellar_image.eps}
    \caption[Mock stellar image of galaxy at z=0 with different feedback
    models]{Mock stellar image of each galaxy at $z=0$.  The top row shows the
    galaxies edge-on, while the bottom shows them face-on.  The no-feedback case
    shows very little disc, while the blastwave feedback case has a thin disc
    with a prominent bulge.  The superbubble galaxy appears nearly bulgeless,
    composed only of a truncated disc. Note also that the superbubble galaxy is
    bluer than the blastwave or no-feedback galaxies, evidence of a younger
    stellar population.}
    \label{stellar_image}
\end{figure*}
\begin{figure*}
    \includegraphics[width=\textwidth]{figures2/column_density.eps}
    \caption[HI column density in a galaxy at z=0 with different feedback models]{HI
    column density for the four test cases at z=0.  The no feedback case has
    exhausted nearly all of the gas within the disc, leaving only diffuse wisps.
    The two superbubble cases (especially with doubled supernova energy) have
    lofted a large amount of gas out of the disc, and some entrained dense
    clumps can be seen in this outflowing material.  The superbubble gas discs
    are much more flocculent than the blastwave disc, and where the feedback
    energy is doubled, the disc is strongly disrupted.}
    \label{column_density}
\end{figure*}

@@

    \includegraphics[width=\textwidth]{figures2/rotation_curve.eps}
    \caption[Rotation curves with different feedback models]{Rotation curves for
    each of our test cases.  As is clear, the superbubble cases have much lower
    central concentrations, giving a a rotation curve that rises to a flat
    $200\; \rm{km/s}$.  The peaked rotation curves in the cases with blastwave
    or no feedback are a result of their failure to remove low angular momentum
    gas at high redshift, giving bulge-dominated, centrally concentrated
    galaxies.}
    \label{rotation_curve}

@@

    \includegraphics[width=\textwidth]{figures2/circularity.eps}

@@

    \includegraphics[width=\textwidth]{figures2/mass_growth.eps}

@@

    \includegraphics[width=\textwidth]{figures2/stellar_fraction.eps}

@@

    \includegraphics[width=\textwidth]{figures2/sfr.eps}

@@

    \includegraphics[width=\textwidth]{figures2/burstiness.eps}

@@

    \includegraphics[width=\textwidth]{figures2/massloading.eps}

@@

    \includegraphics[width=\textwidth]{figures2/net_accretion.eps}
    \caption[Net baryonic accretion for different feedback models]{Net baryonic
    accretion (stars and gas) for each test case.  It is clear that superbubble
    feedback expels baryons much more effectively than the blastwave feedback
    model (although even weak feedback does help somewhat compared to no
    feedback whatsoever).}
    \label{net_accretion}
    \includegraphics[width=\textwidth]{figures2/inflowoutflow.eps}
    \caption[Inflow and outflow rates for different feedback models]{Inflow and
    outflow rates for superbubble (red) and blastwave (blue) run.  The solid
    lines show the total inflow rate, while the dashed and dotted lines show
    rates for cold and hot gas (above/below $10^5\; \rm{K}$) respectively.  }
    \label{inflow_outflow}
    \includegraphics[width=\textwidth]{figures2/angular_momentum_netflux.eps}
    \caption[Net accretion as a function of angular momentum]{In all four test
    cases, including the fiducial superbubble run shown above by the solid
    curve, and the no-feedback case shown by the dotted curve, the vast majority
    of low angular momentum material, with specific angular momentum $ j_z <
    500\; \rm {kpc\; km/s}$, is accreted by $z=2$.  The accretion of high
    angular momentum material, with $j_z > 1500\; \rm{kpc\; km/s}$ rises to peak
    at $z=2$, and continues to accrete $\sim 2\; \rm{M_\odot/yr}$ at $z=0$.  As
    can be seen here, the net flux of low angular momentum material at high
    redshift is suppressed, while the accretion of high angular momentum
    material at low redshift is actually {\it enhanced} by superbubble
    feedback.}
        \label{angular_momentum_netflux}
    \includegraphics[width=\textwidth]{figures2/angular_momentum_outflow.eps}
    \caption[High redshift winds remove low angular momentum gas]{High-redshift
    winds preferentially remove low angular momentum material.  As can be seen
    here, significantly more low angular momentum material is removed by
    superbubble feedback than by the weaker blastwave feedback, but the amount
    of ejected high-angular momentum material is roughly equal.}
        \label{angular_momentum_outflow}
    \includegraphics[width=\textwidth]{figures2/phase.eps}
    \caption[Gas phase diagram for g1536]{Phase diagram of gas in the halo at $z=0$.  The hot, coronal gas
        with temperatures above $10^5\;K$ contains roughly 40\% of the gas mass
        in the halo.  This gas is a mixture of virial-shocked pristine gas,
        which has never been within the interior $0.1R_{vir}$, and outflowing
        material ejected from the galaxy.  This buoyant, high-entropy gas exits
        the galaxy at high temperature, and cools adiabatically as it rises
        through the CGM.  The three colored contours show the major components
        of this hot coronal gas.  Pristine gas, never falling within the
        interior, is shown in blue.  Young superbubbles, not yet having broken out
        of the galaxy, are shown in red.  Outflowing material that was once inside the
        galaxy but is now cooling adiabatically as it rises through the CGM can be seen
        in orange.  The contours show the 1.5\%, 1\%, and 0.5\% levels for the
        total mass in each cut.}
        \label{phase}

\section{Results}
\begin{table*}
    \begin{tabular}{ c c c c c c c}
        \hline
        Simulation & $M_{vir}$ & $M_{gas}$ &
        $M_{star}$  &$M_{bary,0.1vir}$ & $M_{bulge}$ & $M_{disc}$ \\
        \hline
        No Feedback & $7.94\times10^{11}$ & $6.21\times10^{10}$ &
        $7.42\times10^{10}$ & $8.09\times10^{10}$ & $9.34\times10^{9}$ &
        $2.88\times10^{10}$\\
        Blastwave Feedback & $7.99\times10^{11}$ & $8.05\times10^{10}$ &
        $5.11\times10^{10}$ & $7.94\times10^{10}$ & $8.09\times10^{9}$ &
        $1.75\times10^{10}$ \\
        Superbubble Feedback & $8.02\times10^{11}$ & $1.19\times10^{11}$ &
        $1.84\times10^{10}$ & $6.25\times10^{10}$ & $1.14\times10^{9}$ &
        $1.15\times10^{10}$ \\
        Superbubble, $2\times10^{51} erg/SN$ & $7.96\times10^{11}$ &
        $1.20\times10^{11}$ & $1.09\times10^{10}$ &  $4.92\times10^{10}$ & 
        $5.96\times10^{8}$ & $6.98\times10^9$\\
    \end{tabular}
    \caption[Halo Components at $z=0$ for different feedback models]{Halo
    components at $z=0$. $M_{disc}$ and $M_{bulge}$ are the determined by the
    angular momentum of the stars (as detailed below).  All masses are in
    $M_\odot$.}
    \label{properties}
\end{table*}

\subsection{Redshift zero Disc Properties}
As can be seen in Figure~\ref{stellar_image}, the galaxy produced with
superbubble feedback is disc-dominated and blue.  The stellar disc in the case
without feedback is nearly non-existent, with an ellipsoidal morphology.  The
superbubble disc appears somewhat thicker and truncated compared to the disc
produced with blastwave feedback.  The truncation can be seen in the reduced
stellar scale length of the superbubble galaxy, $2.9\;\rm{kpc}$ vs.
$3.8\;\rm{kpc}$ for the superbubble vs. blastwave galaxies.  The thickening
appears to be quantitatively insignificant, however, as both discs have stellar
scale heights of $0.9\;\rm{kpc}$ This may be due to the the disc being disrupted
at large radii, where the surface densities are lower, allowing superbubbles to
grow larger and escape more easily.  The increased feedback case is
interestingly somewhat tilted compared to the rotation of the halo as a whole.

@@

\subsection{Halo Evolution and Star Formation}
Ejecting baryons from the disc is essential to producing galaxies that fit the
$M_*/M_{halo}$ relationship predicted by \citet{Behroozi2013},
\citet{Moster2013} and others.  As Figures~\ref{mass_growth}
and~\ref{stellar_fraction} show, the galaxies either lacking feedback or using
blastwave feedback alone fail to regulate star formation, diverging from the
expected abundance matching relation at $z\sim3$ for the blastwave, and before
$z=5$ without feedback, giving galaxies that lie above the abundance-matching
relationships over nearly their entire history and mass evolution.  With
superbubble feedback, this galaxy lies within the range of observed stellar
masses over its entire evolution, although on the low side of this range at low
redshift.  Arbitrarily increasing feedback energies, despite having reasonable
star formation rates near $z=0$, under produces stars for most cosmic history,
giving stellar masses {\it lower} than predicted by abundance matching.  Stellar
and total masses were calculated for the region inside $R_{vir}$.  As the halo
grows over time, brief reductions in the stellar mass fraction can be seen for
the no-feedback and blastwave feedback halos in Figure~\ref{stellar_fraction},
simply by the accretion of gas and dark matter that has not yet made it to the
galaxy disc.  Once these mergers complete, the stellar fraction rate leaps up
once again because of the new supply of gas.  The relative flatness in this
figure at low redshift is reflected in the relative flatness in the star
formation rate, shown in figure~\ref{sfr}.  This is simply a side effect of the
massive star formation rates at high redshift:  the bulk of star forming gas has
been consumed, and thus star formation has slowed.

@@

\subsection{Outflow Analysis}
Star formation in the disc drives hot, fast-moving outflows from the central star
forming regions.  These outflows have temperatures of $\sim2\times10^7\; \rm{K}$
as they leave the disc, and also entrain some cold material with them.
Typically outflow velocities are a few hundred $\rm{km/s}$, less than the
escape velocity of the halo, but sufficient to propel gas to large radii before
it begins to fall in again.

>>>>

@@

    \includegraphics[width=\textwidth]{figures2/stellar_image.eps}
    \caption[Mock stellar image of galaxy at z=0 with different feedback
    models]{Mock stellar image of each galaxy at $z=0$.  The top row shows the
    galaxies edge-on, while the bottom shows them face-on.  The no-feedback case
    shows very little disc, while the blastwave feedback case has a thin disc
    with a prominent bulge.  The superbubble galaxy appears nearly bulgeless,
    composed only of a truncated disc. Note also that the superbubble galaxy is
    bluer than the blastwave or no-feedback galaxies, evidence of a younger
    stellar population.}
    \label{stellar_image}
\end{figure}
\begin{figure}
    \includegraphics[width=\textwidth]{figures2/column_density.eps}
    \caption[HI column density in a galaxy at z=0 with different feedback models]{HI
    column density for the four test cases at z=0.  The no feedback case has
    exhausted nearly all of the gas within the disc, leaving only diffuse wisps.
    The two superbubble cases (especially with doubled supernova energy) have
    lofted a large amount of gas out of the disc, and some entrained dense
    clumps can be seen in this outflowing material.  The superbubble gas discs
    are much more flocculent than the blastwave disc, and where the feedback
    energy is doubled, the disc is strongly disrupted.}
    \label{column_density}
\end{figure}
\begin{figure}
    \includegraphics[width=0.6\textwidth]{figures2/rotation_curve.eps}
    \caption[Rotation curves with different feedback models]{Rotation curves for
    each of our test cases.  As is clear, the superbubble cases have much lower
    central concentrations, giving a a rotation curve that rises to a flat
    $200\; \rm{km/s}$.  The peaked rotation curves in the cases with blastwave
    or no feedback are a result of their failure to remove low angular momentum
    gas at high redshift, giving bulge-dominated, centrally concentrated
    galaxies.}
    \label{rotation_curve}
\end{figure}

\section{Results}
\subsection{Redshift zero Disc Properties}
\begin{table}
    \scriptsize
    \begin{tabular}{ c c c c c c c}
        \hline
        Simulation & $M_{vir}$ & $M_{gas}$ &
        $M_{star}$  &$M_{bary,0.1vir}$ & $M_{bulge}$ & $M_{disc}$ \\
        \hline
        No Feedback & $7.94\times10^{11}$ & $6.21\times10^{10}$ &
        $7.42\times10^{10}$ & $8.09\times10^{10}$ & $9.34\times10^{9}$ &
        $2.88\times10^{10}$\\
        Blastwave Feedback & $7.99\times10^{11}$ & $8.05\times10^{10}$ &
        $5.11\times10^{10}$ & $7.94\times10^{10}$ & $8.09\times10^{9}$ &
        $1.75\times10^{10}$ \\
        Superbubble Feedback & $8.02\times10^{11}$ & $1.19\times10^{11}$ &
        $1.84\times10^{10}$ & $6.25\times10^{10}$ & $1.14\times10^{9}$ &
        $1.15\times10^{10}$ \\
        Superbubble, $2\times10^{51} erg/SN$ & $7.96\times10^{11}$ &
        $1.20\times10^{11}$ & $1.09\times10^{10}$ &  $4.92\times10^{10}$ & 
        $5.96\times10^{8}$ & $6.98\times10^9$\\
    \end{tabular}
    \caption[Halo Components at $z=0$ for different feedback models]{Halo
    components at $z=0$. $M_{disc}$ and $M_{bulge}$ are the determined by the
    angular momentum of the stars (as detailed below).  All masses are in
    $M_\odot$.}
    \label{properties}
\end{table}

As can be seen in Figure~\ref{stellar_image}, the galaxy produced with
superbubble feedback is disc-dominated and blue.  The stellar disc in the case
without feedback is nearly non-existent, with an ellipsoidal morphology.  The
superbubble disc appears somewhat thicker and truncated compared to the disc
produced with blastwave feedback.  The truncation can be seen in the reduced
stellar scale length of the superbubble galaxy, $2.9\;\rm{kpc}$ vs.
$3.8\;\rm{kpc}$ for the superbubble vs. blastwave galaxies.  The thickening
appears to be quantitatively insignificant, however, as both discs have stellar
scale heights of $0.9\;\rm{kpc}$ This may be due to the the disc being disrupted
at large radii, where the surface densities are lower, allowing superbubbles to
grow larger and escape more easily.  The increased feedback case is
interestingly somewhat tilted compared to the rotation of the halo as a whole.  

@@

    \includegraphics[width=0.6\textwidth]{figures2/circularity.eps}

@@

    \includegraphics[width=0.6\textwidth]{figures2/mass_growth.eps}

@@

    \includegraphics[width=0.6\textwidth]{figures2/stellar_fraction.eps}

@@

    \includegraphics[width=0.6\textwidth]{figures2/sfr.eps}

@@

    \includegraphics[width=0.6\textwidth]{figures2/burstiness.eps}

@@

    \includegraphics[width=0.8\textwidth]{figures2/massloading.eps}

@@

@@

\subsection{Halo Evolution and Star Formation}
\begin{figure}
    \includegraphics[width=0.7\textwidth]{figures2/net_accretion.eps}
    \caption[Net baryonic accretion for different feedback models]{Net baryonic
    accretion (stars and gas) for each test case.  It is clear that superbubble
    feedback expels baryons much more effectively than the blastwave feedback
    model (although even weak feedback does help somewhat compared to no
    feedback whatsoever).}
    \label{net_accretion}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/inflowoutflow.eps}
    \caption[Inflow and outflow rates for different feedback models]{Inflow and
    outflow rates for superbubble (red) and blastwave (blue) run.  The solid
    lines show the total inflow rate, while the dashed and dotted lines show
    rates for cold and hot gas (above/below $10^5\; \rm{K}$) respectively.  }
    \label{inflow_outflow}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/angular_momentum_netflux.eps}
    \caption[Net accretion as a function of angular momentum]{In all four test
    cases, including the fiducial superbubble run shown above by the solid
    curve, and the no-feedback case shown by the dotted curve, the vast majority
    of low angular momentum material, with specific angular momentum $ j_z <
    500\; \rm {kpc\; km/s}$, is accreted by $z=2$.  The accretion of high
    angular momentum material, with $j_z > 1500\; \rm{kpc\; km/s}$ rises to peak
    at $z=2$, and continues to accrete $\sim 2\; \rm{M_\odot/yr}$ at $z=0$.  As
    can be seen here, the net flux of low angular momentum material at high
    redshift is suppressed, while the accretion of high angular momentum
    material at low redshift is actually {\it enhanced} by superbubble
    feedback.}
        \label{angular_momentum_netflux}
\end{figure}
Ejecting baryons from the disc is essential to producing galaxies that fit the
$M_*/M_{halo}$ relationship predicted by \citet{Behroozi2013},
\citet{Moster2013} and others.  As Figures~\ref{mass_growth}
and~\ref{stellar_fraction} show, the galaxies either lacking feedback or using
blastwave feedback alone fail to regulate star formation, diverging from the
expected abundance matching relation at $z\sim3$ for the blastwave, and before
$z=5$ without feedback, giving galaxies that lie above the abundance-matching
relationships over nearly their entire history and mass evolution.  With
superbubble feedback, this galaxy lies within the range of observed stellar
masses over its entire evolution, although on the low side of this range at low
redshift.  Arbitrarily increasing feedback energies, despite having reasonable
star formation rates near $z=0$, under produces stars for most cosmic history,
giving stellar masses {\it lower} than predicted by abundance matching.  Stellar
and total masses were calculated for the region inside $R_{vir}$.  As the halo
grows over time, brief reductions in the stellar mass fraction can be seen for
the no-feedback and blastwave feedback halos in Figure~\ref{stellar_fraction},
simply by the accretion of gas and dark matter that has not yet made it to the
galaxy disc.  Once these mergers complete, the stellar fraction rate leaps up
once again because of the new supply of gas.  The relative flatness in this
figure at low redshift is reflected in the relative flatness in the star
formation rate, shown in figure~\ref{sfr}.  This is simply a side effect of the
massive star formation rates at high redshift:  the bulk of star forming gas has
been consumed, and thus star formation has slowed.

@@

\subsection{Outflow Analysis}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/angular_momentum_outflow.eps}
    \caption[High redshift winds remove low angular momentum gas]{High-redshift
    winds preferentially remove low angular momentum material.  As can be seen
    here, significantly more low angular momentum material is removed by
    superbubble feedback than by the weaker blastwave feedback, but the amount
    of ejected high-angular momentum material is roughly equal.}
        \label{angular_momentum_outflow}
\end{figure}
\begin{figure}
    \includegraphics[width=0.8\textwidth]{figures2/phase.eps}
    \caption[Gas phase diagram for g1536]{Phase diagram of gas in the halo at $z=0$.  The hot, coronal gas
        with temperatures above $10^5\;K$ contains roughly 40\% of the gas mass
        in the halo.  This gas is a mixture of virial-shocked pristine gas,
        which has never been within the interior $0.1R_{vir}$, and outflowing
        material ejected from the galaxy.  This buoyant, high-entropy gas exits
        the galaxy at high temperature, and cools adiabatically as it rises
        through the CGM.  The three colored contours show the major components
        of this hot coronal gas.  Pristine gas, never falling within the
        interior, is shown in blue.  Young superbubbles, not yet having broken out
        of the galaxy, are shown in red.  Outflowing material that was once inside the
        galaxy but is now cooling adiabatically as it rises through the CGM can be seen
        in orange.  The contours show the 1.5\%, 1\%, and 0.5\% levels for the
        total mass in each cut.}
        \label{phase}
\end{figure}
Star formation in the disc drives hot, fast-moving outflows from the central star
forming regions.  These outflows have temperatures of $\sim2\times10^7\; \rm{K}$
as they leave the disc, and also entrain some cold material with them.
Typically outflow velocities are a few hundred $\rm{km/s}$, less than the
escape velocity of the halo, but sufficient to propel gas to large radii before
it begins to fall in again.
